The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-09-13 analysis/paper/paper.qmd
Update c_ngrams check
Update facet names in plot of theses topics

# # Check if concatenated ngrams are retained
# unlist(str_match_all(emu_words$word, "[A-Za-z]+(?:_[A-Za-z]+)+"))
```

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 70
topic_prop_examples <- theta_5[1:N,]
colnames(topic_prop_examples) <- topic_names_5
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(str_sub(rownames(topic_prop_examples), 1, 20))), 
                     variable.name = "topic", id.vars = "document") |> 
  group_by(document) |> 
  mutate(value_max = max(value),
         topic_max = topic[value == value_max])
ggplot(data = vizDataFrame, aes(topic, value, fill = topic_max), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 10) +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d(name = "Topic") +
  labs(title = "Theses as distributions over topics",
       subtitle = "Charts colored by the highest probability")

>>>>

# # Check if concatenated ngrams are retained
# sort(table(unlist(str_match_all(emu_words$word, "[A-Za-z]+(?:_[A-Za-z]+)+"))), decreasing = TRUE)
```

@@

# TODO Replace this with a table containing topics, documents, and theta
#      sorted by theta in decreasing order
# What is the dominant topic in each document?
N = 70
topic_prop_examples <- theta_5[1:N,]
colnames(topic_prop_examples) <- topic_names_5
# TODO change to pivot_longer
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(str_sub(rownames(topic_prop_examples), 1, 20))), 
                     variable.name = "topic", id.vars = "document") |> 
  group_by(document) |> 
  mutate(value_max = max(value),
         topic_max = topic[value == value_max])
ggplot(data = vizDataFrame, aes(topic, value, fill = topic_max), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ as.numeric(document), ncol = 10) +
  theme(legend.position = "bottom") +
  scale_fill_viridis_d(name = "Topic") +
  labs(title = "Theses as distributions over topics",
       subtitle = "Charts colored by the highest probability")
